### 2015-10-09 ThesisJo/derivations.tex
la2pdf commit - 2015:08:17	14:36:33	(Mon17.Aug)
la2pdf commit - 2015:10:09	15:48:03	(Fri 9.Oct)
la2pdf commit - 2015:10:09	20:08:04	(Fri 9.Oct)

@@

>>>>

%  coarse delay adjustment is usually achieved by applying delays to the sensor channels to negate the difference in travel time from the point of interest, and cause the  thereby aligning the phase of the signals coming from that source. Next a set of weights, or window, is applied to the sensors to Finally a set of weights  , which in effect achieve this by applying delays and weigths to the sensor channels to coherently combine signals from the direction of interest.
%

@@

\section{Mathematical Proofs}

\subsection[Proof d/dw\^{}H w\^{}HRw = 2Rw]{Proof: $\frac{\partial}{\partial\w\H} \w\H\R\w = 2\R\w$}

\begin{align}
\w\H\R\w &= \sumb{i=0}{N}w_i^* \sumb{j=0}{N}  R_{ij} w_j \nn
&= \sumb{\substack{i=0\\i\ne k}}{N} w_i^* \sumb{j=0}{N} R_{ij} w_j + w_k^*\sumb{j=0}{N} R_{kj} w_j \nn
&= \sumb{\substack{i=0\\i\ne k}}{N} w_i^* \sumb{\substack{j=0\\j\ne k}}{N} R_{ij} w_j + w_k^*\sumb{j=0}{N} R_{kj} w_j + w_k\sumb{i=0}{N}w_i^* R_{ik} \nn
&= \sumb{\substack{i=0\\i\ne k}}{N} w_i^* \sumb{\substack{j=0\\j\ne k}}{N} R_{ij} w_j + w_k^*\sumb{j=0}{N} R_{kj} w_j + w_k^*\sumb{i=0}{N}w_i R_{ik}^* \nn
&= \sumb{\substack{i=0\\i\ne k}}{N} w_i^* \sumb{\substack{j=0\\j\ne k}}{N} R_{ij} w_j + 2w_k^*\sumb{i=0}{N} R_{ki} w_i
\end{align}
%
Partial differentiation with respect to $\w\H$ then yields:
%
\begin{align}
\frac{\partial}{\partial w_k^*}\;\w\H\R\w
&= \sumb{\substack{i=0\\i\ne k}}{N} w_i^* \sumb{j=0}{N} R_{ij} w_j + w_k^*\sumb{j=0}{N} R_{kj} w_j \nn
&= \sumb{\substack{i=0\\i\ne k}}{N} w_i^* \sumb{j=0}{N} R_{ij} w_j + w_k^*\sumb{j=0}{N} R_{kj} w_j
\end{align}
